Approval and participation index for a voting process

### 2015-04-23 ApresentacoesArtigos/collectiveRanking/paper.tex
terminada primeira versao com as referencias

%------------------------------------------------
% OPTIONAL POSTSCRIPT FONT FILES
%------------------------------------------------

@@

There is a number of other solutions for online collaborative prioritization, such as IdeaScale, Kidling, or any flavor of an Analytic Hierarchy Process (AHP). Authors hope to better formalize possible solutions (and found implementations), maybe through recommendation systems theory~\cite{coursera}.

@@

\bibitem{Versinus}
Fabbri, Renato. "Versinus: a visualization method for graphs in evolution." arXiv preprint arXiv:1412.7311 (2014).

\bibitem{musicArticle}
Fabbri, Renato, et al. "Psychophysics of musical elements in the discrete-time representation of sound." arXiv preprint arXiv:1412.6853 (2014).
%\bibitem{BN}
%M.~Belkin and P.~Niyogi, {\em Using manifold structure for partially
%  labelled classification}, Advances in NIPS, 15 (2003).
%
%\bibitem{BBG:EmbeddingRiemannianManifoldHeatKernel}
%P.~B\'erard, G.~Besson, and S.~Gallot, {\em Embedding {R}iemannian
%  manifolds by their heat kernel}, Geom. and Fun. Anal., 4 (1994),
%  pp.~374--398.
%
%\bibitem{CLAcha1}
%R.R.~Coifman and S.~Lafon, {\em Diffusion maps}, Appl. Comp. Harm. Anal.,
%  21 (2006), pp.~5--30.
%
%\bibitem{DiffusionPNAS}
%R.R.~Coifman, S.~Lafon, A.~Lee, M.~Maggioni, B.~Nadler, F.~Warner, and
%  S.~Zucker, {\em Geometric diffusions as a tool for harmonic analysis and
%  structure definition of data. {P}art {I}: Diffusion maps}, Proc. of Nat.
%  Acad. Sci.,  (2005), pp.~7426--7431.
%
%\bibitem{Clementi:LowDimensionaFreeEnergyLandscapesProteinFolding}
%P.~Das, M.~Moll, H.~Stamati, L.~Kavraki, and C.~Clementi, {\em
%  Low-dimensional, free-energy landscapes of protein-folding reactions by
%  nonlinear dimensionality reduction}, P.N.A.S., 103 (2006), pp.~9885--9890.
%
%\bibitem{DoGri}
%D.~Donoho and C.~Grimes, {\em Hessian eigenmaps: new locally linear
%  embedding techniques for high-dimensional data}, Proceedings of the National
%  Academy of Sciences, 100 (2003), pp.~5591--5596.
%
%\bibitem{DoGri:WhenDoesIsoMap}
%D.~L. Donoho and C.~Grimes, {\em When does isomap recover natural
%  parameterization of families of articulated images?}, Tech. Report Tech. Rep.
%  2002-27, Department of Statistics, Stanford University, August 2002.
%
%\bibitem{GruterWidman:GreenFunction}
%M.~Gr\"uter and K.-O. Widman, {\em The {G}reen function for uniformly
%  elliptic equations}, Man. Math., 37 (1982), pp.~303--342.
%
%\bibitem{Simon:NeumannEssentialSpectrum}
%R.~Hempel, L.~Seco, and B.~Simon, {\em The essential spectrum of neumann
%  laplacians on some bounded singular domains}, 1991.
%
%\bibitem{1}
%Kadison, R.\ V.\ and Singer, I.\ M.\ (1959)
%Extensions of pure states, {\it Amer.\ J.\ Math.\ \bf
%81}, 383-400.
%
%\bibitem{2}
%Anderson, J.\ (1981) A conjecture concerning the pure states of
%$B(H)$ and a related theorem. in {\it Topics in Modern Operator
%Theory}, Birkha\"user, pp.\ 27-43.
%
%\bibitem{3}
%Anderson, J.\ (1979) Extreme points in sets of
%positive linear maps on $B(H)$. {\it J.\ Funct.\
%Anal.\
%\bf 31}, 195-217.
%
%\bibitem{4}
%Anderson, J.\ (1979) Pathology in the Calkin algebra. {\it J.\
%Operator Theory \bf 2}, 159-167.
%
%\bibitem{5}
%Johnson, B.\ E.\ and Parrott, S.\ K.\ (1972) Operators commuting
%with a von Neumann algebra modulo the set of compact operators.
%{\it J.\ Funct.\ Anal.\ \bf 11}, 39-61.
%
%\bibitem{6}
%Akemann, C.\ and Weaver, N.\ (2004) Consistency of a
%counterexample to Naimark's problem. {\it Proc.\ Nat.\ Acad.\
%Sci.\ USA \bf 101}, 7522-7525.
%
%\bibitem{TSL}
%J.~Tenenbaum, V.~de~Silva, and J.~Langford, {\em A global geometric
%  framework for nonlinear dimensionality reduction}, Science, 290 (2000),
%  pp.~2319--2323.
%
%\bibitem{ZhaZha}
%Z.~Zhang and H.~Zha, {\em Principal manifolds and nonlinear dimension
%  reduction via local tangent space alignement}, Tech. Report CSE-02-019,
%  Department of computer science and engineering, Pennsylvania State
%  University, 2002.
\end{thebibliography}

>>>>

\usepackage{hyperref}
%------------------------------------------------
% OPTIONAL POSTSCRIPT FONT FILES
%------------------------------------------------

@@

There is a number of other solutions for online collaborative prioritization, such as IdeaScale, Kidling, or any flavor of an Analytic Hierarchy Process (AHP). Authors hope to better formalize possible solutions (and found implementations), maybe through recommender systems theory~\cite{coursera}.

@@

\bibitem{issue1}
Issue \#19 for implementing priorization algorithm. \url{https://gitlab.com/participa/proposal-app/issues/19}

\bibitem{issue2}
Issue \#29 for implementing priorization algorithm. \url{https://gitlab.com/participa/proposal-app/issues/29}

\bibitem{tabRonald}
Table developed for discussions about approval and participation indexes. Ronald Costa. \url{https://docs.google.com/spreadsheets/d/1Q2uXcuKYOuL0nJdpjXoUaQhjmj6mNv2St7F-pBi_3lw}

\bibitem{pairwise}
  Wiki surveys: Open and quantifiable social data collection,
  Salganik, Matthew J and Levy, Karen EC,
  arXiv preprint arXiv:1202.0500,
  \url{http://arxiv.org/abs/1202.0500}

\bibitem{appgree}
  Appgree software for collective ranking of proposals. \url{http://www.appgree.com}

\bibitem{liquid}
  Through Liquid Democracy to Sustainable Non-Bureaucratic Government,
  Paulin, Alois,
  CeDEM 2014,
  p. 205--217,
  2014, \url{http://research.apaulin.com/research/2014/cedem14-ld-snbg}

\bibitem{agora}
Agora Algorithm, Brazilian social participation community, \url{https://vimeo.com/39135943}

\bibitem{coursera}
Konstan, Joseph A., et al. "Teaching recommender systems at large scale: evaluation and lessons learned from a hybrid MOOC." Proceedings of the first ACM conference on Learning@ scale conference. ACM, 2014. \url{http://dl.acm.org/citation.cfm?id=2566244}

%\bibitem{Versinus}
%Fabbri, Renato. "Versinus: a visualization method for graphs in evolution." arXiv preprint arXiv:1412.7311 (2014).
%
%\bibitem{musicArticle}
%Fabbri, Renato, et al. "Psychophysics of musical elements in the discrete-time representation of sound." arXiv preprint arXiv:1412.6853 (2014).
%\bibitem{BN}
%M.~Belkin and P.~Niyogi, {\em Using manifold structure for partially
%  labelled classification}, Advances in NIPS, 15 (2003).
%
%\bibitem{BBG:EmbeddingRiemannianManifoldHeatKernel}
%P.~B\'erard, G.~Besson, and S.~Gallot, {\em Embedding {R}iemannian
%  manifolds by their heat kernel}, Geom. and Fun. Anal., 4 (1994),
%  pp.~374--398.
%
%\bibitem{CLAcha1}
%R.R.~Coifman and S.~Lafon, {\em Diffusion maps}, Appl. Comp. Harm. Anal.,
%  21 (2006), pp.~5--30.
%
%\bibitem{DiffusionPNAS}
%R.R.~Coifman, S.~Lafon, A.~Lee, M.~Maggioni, B.~Nadler, F.~Warner, and
%  S.~Zucker, {\em Geometric diffusions as a tool for harmonic analysis and
%  structure definition of data. {P}art {I}: Diffusion maps}, Proc. of Nat.
%  Acad. Sci.,  (2005), pp.~7426--7431.
%
%\bibitem{Clementi:LowDimensionaFreeEnergyLandscapesProteinFolding}
%P.~Das, M.~Moll, H.~Stamati, L.~Kavraki, and C.~Clementi, {\em
%  Low-dimensional, free-energy landscapes of protein-folding reactions by
%  nonlinear dimensionality reduction}, P.N.A.S., 103 (2006), pp.~9885--9890.
%
%\bibitem{DoGri}
%D.~Donoho and C.~Grimes, {\em Hessian eigenmaps: new locally linear
%  embedding techniques for high-dimensional data}, Proceedings of the National
%  Academy of Sciences, 100 (2003), pp.~5591--5596.
%
%\bibitem{DoGri:WhenDoesIsoMap}
%D.~L. Donoho and C.~Grimes, {\em When does isomap recover natural
%  parameterization of families of articulated images?}, Tech. Report Tech. Rep.
%  2002-27, Department of Statistics, Stanford University, August 2002.
%
%\bibitem{GruterWidman:GreenFunction}
%M.~Gr\"uter and K.-O. Widman, {\em The {G}reen function for uniformly
%  elliptic equations}, Man. Math., 37 (1982), pp.~303--342.
%
%\bibitem{Simon:NeumannEssentialSpectrum}
%R.~Hempel, L.~Seco, and B.~Simon, {\em The essential spectrum of neumann
%  laplacians on some bounded singular domains}, 1991.
%
%\bibitem{1}
%Kadison, R.\ V.\ and Singer, I.\ M.\ (1959)
%Extensions of pure states, {\it Amer.\ J.\ Math.\ \bf
%81}, 383-400.
%
%\bibitem{2}
%Anderson, J.\ (1981) A conjecture concerning the pure states of
%$B(H)$ and a related theorem. in {\it Topics in Modern Operator
%Theory}, Birkha\"user, pp.\ 27-43.
%
%\bibitem{3}
%Anderson, J.\ (1979) Extreme points in sets of
%positive linear maps on $B(H)$. {\it J.\ Funct.\
%Anal.\
%\bf 31}, 195-217.
%
%\bibitem{4}
%Anderson, J.\ (1979) Pathology in the Calkin algebra. {\it J.\
%Operator Theory \bf 2}, 159-167.
%
%\bibitem{5}
%Johnson, B.\ E.\ and Parrott, S.\ K.\ (1972) Operators commuting
%with a von Neumann algebra modulo the set of compact operators.
%{\it J.\ Funct.\ Anal.\ \bf 11}, 39-61.
%
%\bibitem{6}
%Akemann, C.\ and Weaver, N.\ (2004) Consistency of a
%counterexample to Naimark's problem. {\it Proc.\ Nat.\ Acad.\
%Sci.\ USA \bf 101}, 7522-7525.
%
%\bibitem{TSL}
%J.~Tenenbaum, V.~de~Silva, and J.~Langford, {\em A global geometric
%  framework for nonlinear dimensionality reduction}, Science, 290 (2000),
%  pp.~2319--2323.
%
%\bibitem{ZhaZha}
%Z.~Zhang and H.~Zha, {\em Principal manifolds and nonlinear dimension
%  reduction via local tangent space alignement}, Tech. Report CSE-02-019,
%  Department of computer science and engineering, Pennsylvania State
%  University, 2002.
\end{thebibliography}
